Modeling 2024 U.S. Presidential Polling Trends

### 2024-10-29 paper/paper.qmd
Made final change according to peer review

---
title: "Modeling 2024 U.S. Presidential Polling Trends"
subtitle: "Biden’s Steady Support and Harris’s Fluctuations Across Time, Pollsters, and Regions"
author: 
  - Mandy He
  - Wendy Yuan
thanks: "Code and data are available at: https://github.com/MandyHe7/US-Election.git."
date: November 5, 2024
date-format: long
abstract: "This paper looks at polling data from the 2024 U.S. Presidential election to see how candidate support changes and what factors affect polling results. We found that Biden’s support stayed steady, while Harris’s numbers fluctuated more, with differences across time, pollsters, and regions. These findings show that polling methods and location are important in predicting election results. Understanding these trends helps give a clearer view of public opinion before the election, leading to more accurate predictions."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

library(tidyverse)
library(dplyr)
library(readr)
library(ggplot2)
library(janitor)
library(lubridate)
library(broom)
library(modelsummary)
library(rstanarm)
library(splines)

@@

This paper estimates trends in polling support over time and analyzes the factors that contribute to variations in candidate support. We use data from FiveThirtyEight’s U.S. Presidential election polls, collected from pollsters such as YouGov and Siena/NYT. The analysis models polling percentages for each candidate, considering variables such as polling methods, sample size, and region. These variables are examined to better understand how they influence polling outcomes and improve the accuracy of election predictions.

The results show clear trends in candidate support leading up to the election, with differences based on pollster methods, geography, and timing. These findings are important for improving election forecasting by providing a clearer view of how public opinion changes as the election date approaches.

The remainder of the paper is structured as follows: @sec-data details the data and measurement process. @sec-Methodology describes the methodology, including linear and Bayesian models. @sec-Results presents the results, highlighting trends in polling, and @sec-Discussion discusses the implications of the findings for future election forecasting and research.

@@

We use the statistical programming language R [@citeR] to analyze polling data sourced from FiveThirtyEight’s U.S. Presidential election polls [@fivethirtyeight], collected by organizations like YouGov and Siena/NYT through online surveys and phone interviews. The dataset includes key details such as pollster, methodology, sample size, and location, allowing us to track how public opinion shifts over time and across regions. After cleaning the data for accuracy, we analyze trends in candidate support using the outcome variable pct (polling percentage) and predictor variables like pollster, methodology, and state to model and forecast public opinion trends as the election approaches.

@@

Once this data is collected, it’s cleaned to ensure accuracy, removing any inconsistencies or missing values. This allows us to analyze and track how public opinion changes over time and in different regions, turning individual responses into a clear and usable dataset.

@@

- pollster: Identifies the polling organization (e.g., YouGov, Siena/NYT). Different pollsters may use varied methodologies, which can introduce variability in results.
- numeric_grade: Reflects the grading assigned to pollsters by FiveThirtyEight, based on their historical accuracy and reliability.
- methodology: Specifies the polling method used (e.g., Online Panel, Live Phone), which can influence the type of respondents and the accuracy of the poll.
- state: Indicates the region or national focus of the poll, capturing geographical differences in voter behavior.
- sample_size: Represents the number of respondents in each poll, affecting the poll's margin of error and statistical reliability.
- start_date and end_date: Capture the timeframe in which the poll was conducted, enabling the analysis of trends over time.

These variables allow us to model polling percentages and forecast trends, taking into account factors such as methodology, sample size, and regional variations.

@@

We used R (R Core Team 2023) to process polling data for the 2024 U.S. Presidential Election from [@fivethirtyeight]. The data includes results across demographic groups and time periods. Missing values were addressed, and dummy variables created for categorical predictors like region and pollster. Post-stratification weighting ensured the sample represented the U.S. population, reducing bias.

@@

We tested various regression models to predict candidate vote percentages, using predictors like polling date, candidate, and pollster. Models ranged from simple linear regressions to Bayesian models, incorporating historical election data through Bayesian priors.

@@

We use the statistical programming language R [@citeR] and the following packages: tidyverse, dplyr, readr, ggplot2, janitor, lubridate, broom, modelsummary, rstanarm, and splines.

@@

```{r}
#| warning: false
#| message: false
#| label: fig-figure1
#| fig-cap: "illustrates a simple linear regression between end date and pct, showing a positive trend with a noticeable dip in the middle."
#| fig_caption: true
#| echo: false

@@

# Plots poll estimates and overall smoothing
base_plot +
  geom_point() +
  geom_smooth()+
  labs(title = "Election Trends: Regression of End Date and Respondents of Vote")
```

@fig-figure1 illustrates a simple linear regression between end date and pct. It shows a positive trend between the variable but with a noticeable dip around the middle of the X-axis. This dip may indicate some underlying complexity that the simple linear model doesn’t fully capture, but the model does a reasonable job fitting the general positive direction of the data. The regression line captures this linear relationship, with most data points clustering near the line, suggesting a moderate fit. The confidence interval shows some uncertainty at extreme values, where the data becomes more dispersed.

```{r}
#| warning: false
#| message: false
#| label: fig-figure2
#| fig-cap: "Shows a linear regression applied to multiple subsets of the data using facet wrap. Each panel represents a different pollster, with regression lines indicating a generally consistent positive trend, despite some dips."
#| fig_caption: true
#| echo: false

# Facet by pollster
base_plot +
  geom_point() +
  geom_smooth() +
  facet_wrap(vars(pollster))+
  labs(title = "Election Trends: Linear Regression Across Pollster Subsets")
```

@fig-figure2 shows a linear regression applied to multiple subsets of the data using facet wrap. Each panel represents a different pollsters and the regression line within each panel shows a generally consistent positive trend across most subsets - although there are some dips in the trend. Some subsets, like YouGov, have more data points than others, leading to more robust lines with narrower confidence intervals. The individual panels help highlight how the relationship between end date and pct across different pollster,  revealing subtle variations between groups.

```{r}
#| warning: false
#| message: false
#| label: fig-figure3
#| fig-cap: "uses facet wrap to show linear regression across various states. Each panel reveals a linear relationship, with clearer trends in panels with more data points."
#| fig_caption: true
#| echo: false

# Facet by state
base_plot +
  geom_point() +
  geom_smooth() +
  facet_wrap(vars(state))+
  labs(title = "Election Trends: Linear Regression Across States")
```

@fig-figure3 uses facet wrap to apply a linear regression across various states. Each panel depicts a clear linear relationship within its subset, with a up and down wave trend in most. Some panels, particularly those with more data points, show stronger, clearer lines, while others may have flatter trends or greater variability due to smaller sample sizes. The use of facet wrap here provides a clear comparison across groups, making it easy to see where the linear relationship holds strongly and where it varies.

@@

```{r}
#| warning: false
#| message: false
#| label: fig-figure4
#| fig-cap: "illustrates a Bayesian model showing a moderate upward trend, where percentage increases with end date."
#| fig_caption: true
#| echo: false

# Plot the spline fit
ggplot(polling_data, aes(x = end_date, y = pct, color = pollster)) +
  geom_point() +
  geom_line(
    data = pred_summary,
    aes(x = end_date, y = pred_mean),
    color = "blue",
    inherit.aes = FALSE
  ) +
  geom_ribbon(
    data = pred_summary,
    aes(x = end_date, ymin = pred_lower, ymax = pred_upper),
    alpha = 0.2,
    inherit.aes = FALSE
  ) +
  labs(
    x = "Days since earliest poll",
    y = "Percentage",
    title = "Poll Percentage over Time with Spline Fit"
  ) +
  theme_minimal()
```

@@

```{r}
#| warning: false
#| message: false
#| label: fig-figure5
#| fig-cap: "presents a Bayesian model with color-coded points for different states."
#| fig_caption: true
#| echo: false

# Plot the spline fit
ggplot(polling_data_2, aes(x = end_date, y = pct, color = state)) +
  geom_point() +
  geom_line(
    data = pred_summary_2,
    aes(x = end_date, y = pred_mean),
    color = "blue",
    inherit.aes = FALSE
  ) +
  geom_ribbon(
    data = pred_summary_2,
    aes(x = end_date, ymin = pred_lower, ymax = pred_upper),
    alpha = 0.2,
    inherit.aes = FALSE
  ) +
  labs(
    x = "Days since earliest poll",
    y = "Percentage",
    title = "Poll Percentage over Time with Spline Fit"
  ) +
  theme_minimal()
```

@@

@@

@fig-figure2 uses a linear model with facet wrap to illustrate the polling trends for Biden (blue) and Harris (orange) across different pollsters. Each panel represents the polling data from a specific pollster, showing how candidate support varied over time from 2022 to 2024.

@@

@fig-figure3 shows the polling trends for Biden (blue) and Harris (orange) across various U.S. states using a linear model with facet wrap. Each panel represents a separate state or district, allowing for comparison of candidate support trends from 2022 to 2024. The National panel includes polls that do not have state-specific data, providing a broader, generalized view of national polling trends.

@@

@@

# Appendix {-}

@@

YouGov is a widely recognized international polling firm known for its political forecasting, especially through its "poll-of-polls" methodology, which aggregates results from numerous individual surveys. YouGov primarily utilizes online panel polling, offering timely and cost-effective results, especially for U.S. presidential elections. Below is a detailed exploration of YouGov's polling methodology.

@@

+ Population: YouGov’s target population consists of U.S. likely voters, defined by their eligibility and likelihood to vote, assessed through past voting behavior, voter registration, and expressed intent.
+ Frame: The sampling frame is YouGov’s online panel, which includes millions of U.S. residents recruited through various methods. The panel is stratified and weighted to represent key demographics such as age, gender, race, education, and region.
+ Sample: YouGov uses non-probability sampling from its panel, adjusting for biases using sophisticated weighting to reflect the U.S. electorate's composition.

@@

+ YouGov recruits panelists through:

  + Targeted online ads: Ads across websites and social media attract diverse participants.
  + Affiliate marketing: Collaborations with other websites help reach a broad audience.
  + Incentives: Respondents earn points for surveys, increasing participation and retention.

@@

- Advantages:
  - Cost-effectiveness: Online panels are cheaper than traditional phone surveys.
  - Speed: Surveys are completed quickly online.
  - Targeting: Specific groups, such as likely voters, can be efficiently targeted.

- Disadvantages:
  - Non-probability sample: Not all individuals have an equal chance of being selected, risking bias.
  - Internet access bias: Those without internet access may be underrepresented, skewing results,    - particularly for older or lower-income demographics.

@@

+ Incentivizes participation with rewards to increase survey completion.
+ Sends follow-ups for longer surveys, reminding respondents to complete them.
+ Applies weighting to adjust for differential non-response (e.g., giving more weight to younger voters if they are underrepresented).
+ Despite these efforts, some non-response bias may persist, as those opting out may differ systematically from respondents (e.g., lower political engagement).

@@

+ Strengths:
  + Clarity: Questions are designed for consistency in interpretation.
  + Pre-testing: Surveys are often tested with smaller groups to refine clarity and accuracy.
  + Flexibility: Questions are adapted to political events, maintaining relevance.

+ Weaknesses:
  + Limited depth: Online surveys favor simpler, multiple-choice questions, limiting nuanced responses.
  + Response fatigue: Frequent survey participation may cause rushed or less thoughtful responses.
  + Exclusion of offline participants: Individuals without internet access are excluded, impacting representativeness, particularly in underserved demographics.

@@

# Appendix B: Idealized Methodology and Survey
**Overview**

With a $100K budget, the objective of this survey is to forecast the outcome of the upcoming U.S. presidential election using a robust sampling strategy, respondent recruitment process, and careful poll aggregation techniques. This methodology is designed to minimize bias and ensure a representative sample that accurately reflects the voting population.

@@

+ Age: Ensure a balanced representation across different age groups (e.g., 18-29, 30-44, 45-64, 65+).
+ Gender: Include a balanced proportion of male and female respondents, and allow space for non-binary respondents.
+ Race/Ethnicity: Ensure representation of major racial and ethnic groups, including White, Black, Hispanic/Latino, Asian, and other minorities.
+ Education: Include respondents with various educational backgrounds (no high school, high school graduate, college graduate, post-graduate education).
+ Region: Sample respondents from different geographic regions (Northeast, Midwest, South, West) to capture regional variations in voting behavior.
+ Sample Size: Given the budget constraints and the need for statistical reliability, the survey would target a sample size of 5,000 respondents, which allows for meaningful subgroup analysis while keeping costs manageable. This should provide a margin of error around ±1.5% at a 95% confidence level.

@@

+ Online recruitment via targeted ads: Similar to YouGov, targeted ads on social media platforms (e.g., Facebook, Instagram, YouTube) and websites can be used to attract a broad range of respondents. Ads will be tailored to reach different demographic groups based on age, region, and other factors.
+ Email outreach to existing voter databases: Leveraging voter registration lists and databases (where legally permissible) will allow for targeted invitations to participate in the survey.
+ Incentives: Offering incentives, such as entry into a lottery or digital rewards, will increase the participation rate and reduce non-response bias.

Given the budget, $80,000 will be allocated for recruitment efforts and respondent compensation, including targeted online ads and incentives for participants.

@@

+ Captcha verification: This will prevent bots from filling out the survey.
+ Email and phone verification: Respondents will be required to verify their email or phone number to ensure that each respondent is unique.
+ Cross-verification with voter rolls: For respondents who voluntarily provide voter registration details, cross-checking with public voter rolls can validate their voting eligibility.
+ Time tracking and completion rate monitoring: To detect inattentive or rushed responses, the time spent on each question will be tracked, and surveys completed unusually quickly will be flagged for further review.

@@

+ Public polling data: In addition to this survey, data from other reputable pollsters (like YouGov, Ipsos, etc.) will be aggregated.
+ Weighting and adjusting: Each poll's results will be weighted based on its sample size, methodological rigor, and recency. Larger, more recent, and methodologically sound polls will have a greater influence on the final aggregated forecast.
+ Adjustments for known biases: If a particular demographic is underrepresented (e.g., younger voters, rural voters), post-stratification weighting will be applied to ensure the aggregate data reflects the overall voting population.

@@

+ Recruitment (online ads and outreach): $60,000
+ Incentives for respondents: $20,000
+ Survey development and data validation: $10,000
+ Poll aggregation and analysis tools: $10,000

@@

+ Introduction: A brief explanation of the survey’s purpose, ensuring that respondents understand its relevance and importance.
+ Demographic questions: These questions will collect essential data on the respondents’ age, gender, race/ethnicity, education, and region.
+ Political questions: The core section will ask about voting intent, candidate preference, party affiliation, and important political issues. These questions will be designed to minimize bias and allow for nuanced responses (e.g., Likert scales, multiple-choice options).
+ Verification and consent: Respondents will be asked to verify their information and give consent for data use.

@@

+ Question clarity and neutrality: The questions will be carefully worded to avoid leading responses or introducing bias.
+ Ordering of questions: Demographic questions will be asked first to set a neutral tone before moving into political questions.
+ Pilot testing: Before full deployment, the survey will be tested on a small sample to ensure clarity and to refine any confusing questions.

@@

>>>>

---
title: "Modeling 2024 U.S. Presidential Polling Trends"
subtitle: "Democrats Show Strong Support Leading Up to the Election, with Biden's Steady Backing and Harris's Fluctuations Across Regions and Polls."
author: 
  - Mandy He
  - Wendy Yuan
thanks: "Code and data are available at: https://github.com/MandyHe7/US-Election.git."
date: November 4, 2024
date-format: long
abstract: "This paper looks at polling data from the 2024 U.S. Presidential election to see how candidate support changes and what factors affect polling results. We found that Biden’s support remained steady, while Harris’s numbers fluctuated, especially in certain states and under specific pollsters. These finding shows that the Democrats appear to be in a strong position heading into the election. Used alongside election predictions, these insights help clarify the broader scope of Democratic support leading up to the election."
format:
  pdf:
    toc: true
    toc-location: before 
    number-sections: true
bibliography: references.bib
---

@@

library(tidyverse)
library(dplyr)
library(readr)
library(ggplot2)
library(janitor)
library(lubridate)
library(broom)
library(modelsummary)
library(rstanarm)
library(splines)
library(knitr)
library(kableExtra)

@@

This paper does not attempt to forecast the election outcome. Instead, it examines trends in polling support over time and analyzes the factors that contribute to variations in candidate support. Using data from FiveThirtyEight’s U.S. Presidential election polls, collected from pollsters such as YouGov and Siena/NYT, we model polling percentages for each candidate, considering variables like pollster and region. By exploring these variables, we aim to enhance our understanding of how they affect polling results.

We focus on analyzing trends in polling data rather than forecasting the election outcome to gain a deeper understanding of how and why public opinion changes over time. By examining trends, we can see how specific events, regions, and campaign efforts impact voter preferences, providing insights that pure forecasting might miss. Trend analysis also avoids the need for assumptions about future behavior, giving us a clearer picture of the factors that shape current voter support. This approach helps campaigns and analysts recognize consistent patterns in support, guiding more targeted strategies without relying on uncertain predictions.

The results show clear trends in candidate support leading up to the election, with differences based on pollster methods, geography, and timing. These findings provide valuable insights into the dynamics of public opinion during the election period, rather than making predictions about the outcome.

The remainder of the paper is structured as follows: @sec-data details the data and measurement process. @sec-Methodology describes the methodology, including linear and Bayesian models. @sec-Results presents the results, highlighting trends in polling, and @sec-Discussion considers the implications of these results for future research on polling and public opinion.

@@

We use the statistical programming language R [@citeR] to analyze polling data sourced from FiveThirtyEight’s U.S. Presidential election polls [@fivethirtyeight], collected by organizations like YouGov and Siena/NYT through online surveys and phone interviews. The dataset includes details such as pollster, methodology, sample size, and location, allowing us to track how public opinion shifts over time and across regions. After cleaning the data for accuracy, we analyze trends in candidate support using the outcome variable pct (polling percentage) and predictor variables like pollster and state to model and forecast public opinion trends as the election approaches.

@@

Once this data is collected, it’s cleaned to ensure accuracy by selecting numerical grade that is equal to 3, removing any inconsistencies or missing values. This allows us to analyze and track how public opinion changes over time and in different regions, turning individual responses into a clear and usable dataset.

@@

-   pollster: Identifies the polling organization (e.g., YouGov, Siena/NYT). Different pollsters may use varied methodologies, which can introduce variability in results.
-   state: Indicates the region or national focus of the poll, capturing geographical differences in voter behavior.
-   end_date: Capture the timeframe in which the poll was conducted, enabling the analysis of trends over time.

These variables allow us to model polling percentages and forecast trends, taking into account factors such as pollster and regional variations. A summary statistics for predictor variables can be found in @sec-appc.

@@

We used R [@citeR] to process polling data for the 2024 U.S. Presidential Election from [@fivethirtyeight]. The data includes results across demographic groups and time periods. Missing values were addressed, and dummy variables created for categorical predictors like region and pollster. Post-stratification weighting ensured the sample represented the U.S. population, reducing bias.

@@

We tested various regression models to predict candidate vote percentages, using predictors like polling date, candidate, and pollster. Models ranged from simple linear regressions to Bayesian models, incorporating historical election data through Bayesian priors. We chose to use simple linear regression and Bayesian models instead of multiple regression due to the low R-squared values obtained from the multiple regression analysis, which indicated that they do not provide significant insights see @sec-appd.

## Simple Linear Regression

We are performing a regression analysis of PCT with respect to the end date. The following is the simple linear regression equation $pct = \alpha + \beta_1 \cdot \text{end\_date} +\epsilon$.

@@

We use the statistical programming language R [@citeR] and the following packages: tidyverse [@tidyverse], dplyr [@dplyr], readr [@readr], ggplot2 [@ggplot2], janitor [@janitor], lubridate [@lubridate], broom [@broom], modelsummary [@modelsummary], rstanarm [@rstanarm], and splines [@splines], knitr [@knitr], kableExtra [@kableExtra].

@@

```{r}
#| warning: false
#| message: false
#| label: fig-figure1
#| fig-cap: "Simple linear regression between end date and precentage of respondent votes, showing a positive trend for Democrats with a noticeable dip in the middle."
#| fig_caption: true
#| echo: false

@@

# Plots poll estimates and overall smoothing
base_plot +
  geom_point() +
  geom_smooth(alpha = 0.3)
```

@fig-figure1 illustrates a simple linear regression between end date and pct. It shows a positive trend between the variable but with a noticeable dip around the middle. This dip may indicate some underlying complexity that the simple linear model doesn’t fully capture, but the model does a reasonable job fitting the general positive direction of the data. The regression line captures this linear relationship, with most data points clustering near the line, suggesting a moderate fit. The confidence interval shows some uncertainty at extreme values, where the data becomes more dispersed.

```{r}
#| warning: false
#| message: false
#| label: fig-figure2
#| fig-cap: "Linear regression applied to multiple subsets of the data. Each panel represents a different pollster, with regression lines indicating a generally consistent positive trend."
#| fig_caption: true
#| echo: false

# Facet by pollster
base_plot +
  geom_point() +
  geom_smooth(alpha = 0.3) +
  facet_wrap(vars(pollster))
```

@fig-figure2 shows a linear regression applied to multiple subsets of the data. Each panel represents a different pollsters and the regression line within each panel shows a generally consistent positive trend across most subsets - although there are some dips in the trend. Some subsets, like YouGov, have more data points than others, leading to more robust lines with narrower confidence intervals. The individual panels help highlight how the relationship between end date and pct across different pollster, revealing subtle variations between groups.

```{r}
#| warning: false
#| message: false
#| label: fig-figure3
#| fig-cap: "Linear regression across various states. Each panel reveals a linear relationship with clearer trends."
#| fig_caption: true
#| echo: false

# Facet by state
base_plot +
  geom_point() +
  geom_smooth(alpha = 0.3) +
  facet_wrap(vars(state)) +
  theme(axis.text.x = element_text(angle = 45))
```

@fig-figure3 apply a linear regression across various states. Each panel depicts a clear linear relationship within its subset, with a up and down wave trend in most. Some panels, particularly those with more data points, show stronger, clearer lines, while others may have flatter trends or greater variability due to smaller sample sizes. This provides a clear comparison across groups, making it easy to see where the linear relationship holds strongly and where it varies.

@@

```{r}
#| warning: false
#| message: false
#| label: fig-figure4
#| fig-cap: "Bayesian model using spline fit to show a moderate upward trend, where percentage increases over time."
#| fig_caption: true
#| echo: false

# Plot the spline fit
ggplot(polling_data, aes(x = end_date, y = pct, color = pollster)) +
  geom_point() +
  geom_line(
    data = pred_summary,
    aes(x = end_date, y = pred_mean),
    color = "blue",
    inherit.aes = FALSE
  ) +
  geom_ribbon(
    data = pred_summary,
    aes(x = end_date, ymin = pred_lower, ymax = pred_upper),
    alpha = 0.2,
    inherit.aes = FALSE
  ) +
  labs(
    x = "Days since earliest poll",
    y = "Percentage"
  ) +
  theme_minimal()
```

@@

```{r}
#| warning: false
#| message: false
#| label: fig-figure5
#| fig-cap: "Bayesian model using spline fit with color-coded points for different states showing a moderate upward trend."
#| fig_caption: true
#| echo: false

# Plot the spline fit
ggplot(polling_data_2, aes(x = end_date, y = pct, color = state)) +
  geom_point() +
  geom_line(
    data = pred_summary_2,
    aes(x = end_date, y = pred_mean),
    color = "blue",
    inherit.aes = FALSE
  ) +
  geom_ribbon(
    data = pred_summary_2,
    aes(x = end_date, ymin = pred_lower, ymax = pred_upper),
    alpha = 0.2,
    inherit.aes = FALSE
  ) +
  labs(
    x = "Days since earliest poll",
    y = "Percentage"
  ) +
  theme_minimal()
```

@@

Furthermore, Harris’s polling fluctuations reflect Keyes’s [@reallifemag2023] idea of "data violence," which suggests that standard polling methods may unintentionally reinforce narrow or inconsistent views across different demographic groups. Keyes’s focus on using diverse data sources could help reduce these biases and offer a more accurate picture of candidate support among various population segments.

@@

@fig-figure2 uses a linear model to illustrate the polling trends for Biden (blue) and Harris (orange) across different pollsters. Each panel represents the polling data from a specific pollster, showing how candidate support varied over time from 2022 to 2024.

@@

@fig-figure3 shows the polling trends for Biden (blue) and Harris (orange) across various U.S. states using a linear model. Each panel represents a separate state or district, allowing for comparison of candidate support trends from 2022 to 2024. The National panel includes polls that do not have state-specific data, providing a broader, generalized view of national polling trends.

@@

To improve our paper, we can draw on the insights of Neyman [@neyman1934two] and Keyes [@reallifemag2023]. Neyman’s work highlights the value of stratified sampling, which could guide us in making samples more representative across demographic groups, ultimately strengthening our forecasts. We could incorporate voter demographics and turnout probabilities data to enhance our model’s accuracy. Keyes emphasizes the ethical importance of using diverse data sources. Applying this to our polling methods would help ensure fair representation across various demographics and viewpoints. Finally, expanding the analysis to include more pollsters and accounting for the electoral college’s role would provide a more comprehensive view of election outcomes, not limited to the popular vote alone.

@@

@@

YouGov is a widely recognized international polling firm known for its political forecasting, especially through its "poll-of-polls" methodology, which aggregates results from numerous individual surveys[@yougov]. YouGov primarily utilizes online panel polling, offering timely and cost-effective results, especially for U.S. presidential elections. According to Cirone and Spirling’s [@cirone] concept of "methodological awareness" is important here, as understanding how each pollster’s methods affect their results can help create a clearer view of national support trends. Below is a detailed exploration of YouGov's polling methodology [@yougov_methodology].

@@

-   Population: YouGov’s target population consists of U.S. likely voters, defined by their eligibility and likelihood to vote, assessed through past voting behavior, voter registration, and expressed intent.
-   Frame: The sampling frame is YouGov’s online panel, which includes millions of U.S. residents recruited through various methods. The panel is stratified and weighted to represent key demographics such as age, gender, race, education, and region.
-   Sample: YouGov uses non-probability sampling from its panel, adjusting for biases using sophisticated weighting to reflect the U.S. electorate's composition.

@@

-   YouGov recruits panelists through:

    -   Targeted online ads: Ads across websites and social media attract diverse participants.
    -   Affiliate marketing: Collaborations with other websites help reach a broad audience.
    -   Incentives: Respondents earn points for surveys, increasing participation and retention.

@@

-   Advantages:
    -   Cost-effectiveness: Online panels are cheaper than traditional phone surveys.
    -   Speed: Surveys are completed quickly online.
    -   Targeting: Specific groups, such as likely voters, can be efficiently targeted.
-   Disadvantages:
    -   Non-probability sample: Not all individuals have an equal chance of being selected, risking bias.
    -   Internet access bias: Those without internet access may be underrepresented, skewing results, - particularly for older or lower-income demographics.

@@

-   Incentivizes participation with rewards to increase survey completion.
-   Sends follow-ups for longer surveys, reminding respondents to complete them.
-   Applies weighting to adjust for differential non-response (e.g., giving more weight to younger voters if they are underrepresented).
-   Despite these efforts, some non-response bias may persist, as those opting out may differ systematically from respondents (e.g., lower political engagement).

@@

-   Strengths:
    -   Clarity: Questions are designed for consistency in interpretation.
    -   Pre-testing: Surveys are often tested with smaller groups to refine clarity and accuracy.
    -   Flexibility: Questions are adapted to political events, maintaining relevance.
-   Weaknesses:
    -   Limited depth: Online surveys favor simpler, multiple-choice questions, limiting nuanced responses.
    -   Response fatigue: Frequent survey participation may cause rushed or less thoughtful responses.
    -   Exclusion of offline participants: Individuals without internet access are excluded, impacting representativeness, particularly in underserved demographics.

@@

# Appendix B: Idealized Methodology and Survey

**Overview**

With a \$100K budget, the objective of this survey is to forecast the outcome of the upcoming U.S. presidential election using a robust sampling strategy, respondent recruitment process, and careful poll aggregation techniques. This methodology is designed to minimize bias and ensure a representative sample that accurately reflects the voting population.

@@

-   Age: Ensure a balanced representation across different age groups (e.g., 18-29, 30-44, 45-64, 65+).
-   Gender: Include a balanced proportion of male and female respondents, and allow space for non-binary respondents.
-   Race/Ethnicity: Ensure representation of major racial and ethnic groups, including White, Black, Hispanic/Latino, Asian, and other minorities.
-   Education: Include respondents with various educational backgrounds (no high school, high school graduate, college graduate, post-graduate education).
-   Region: Sample respondents from different geographic regions (Northeast, Midwest, South, West) to capture regional variations in voting behavior.
-   Sample Size: Given the budget constraints and the need for statistical reliability, the survey would target a sample size of 5,000 respondents, which allows for meaningful subgroup analysis while keeping costs manageable. This should provide a margin of error around ±1.5% at a 95% confidence level.

@@

-   Online recruitment via targeted ads: Similar to YouGov, targeted ads on social media platforms (e.g., Facebook, Instagram, YouTube) and websites can be used to attract a broad range of respondents. Ads will be tailored to reach different demographic groups based on age, region, and other factors.
-   Email outreach to existing voter databases: Leveraging voter registration lists and databases (where legally permissible) will allow for targeted invitations to participate in the survey.
-   Incentives: Offering incentives, such as entry into a lottery or digital rewards, will increase the participation rate and reduce non-response bias.

Given the budget, \$80,000 will be allocated for recruitment efforts and respondent compensation, including targeted online ads and incentives for participants.

@@

-   Captcha verification: This will prevent bots from filling out the survey.
-   Email and phone verification: Respondents will be required to verify their email or phone number to ensure that each respondent is unique.
-   Cross-verification with voter rolls: For respondents who voluntarily provide voter registration details, cross-checking with public voter rolls can validate their voting eligibility.
-   Time tracking and completion rate monitoring: To detect inattentive or rushed responses, the time spent on each question will be tracked, and surveys completed unusually quickly will be flagged for further review.

@@

-   Public polling data: In addition to this survey, data from other reputable pollsters (like YouGov, Ipsos, etc.) will be aggregated.
-   Weighting and adjusting: Each poll's results will be weighted based on its sample size, methodological rigor, and recency. Larger, more recent, and methodologically sound polls will have a greater influence on the final aggregated forecast.
-   Adjustments for known biases: If a particular demographic is underrepresented (e.g., younger voters, rural voters), post-stratification weighting will be applied to ensure the aggregate data reflects the overall voting population.

@@

-   Recruitment (online ads and outreach): \$60,000
-   Incentives for respondents: \$20,000
-   Survey development and data validation: \$10,000
-   Poll aggregation and analysis tools: \$10,000

@@

-   Introduction: A brief explanation of the survey’s purpose, ensuring that respondents understand its relevance and importance.
-   Demographic questions: These questions will collect essential data on the respondents’ age, gender, race/ethnicity, education, and region.
-   Political questions: The core section will ask about voting intent, candidate preference, party affiliation, and important political issues. These questions will be designed to minimize bias and allow for nuanced responses (e.g., Likert scales, multiple-choice options).
-   Verification and consent: Respondents will be asked to verify their information and give consent for data use.

@@

-   Question clarity and neutrality: The questions will be carefully worded to avoid leading responses or introducing bias.
-   Ordering of questions: Demographic questions will be asked first to set a neutral tone before moving into political questions.
-   Pilot testing: Before full deployment, the survey will be tested on a small sample to ensure clarity and to refine any confusing questions.

@@

# Appendix C: Summary Statistics for Predictor Variables {#sec-appc}

```{r}
#| warning: false
#| message: false
#| label: fig-figure6
#| fig-cap: "Summary Statistics for Predictor Variables"
#| fig_caption: true
#| echo: false

# Ensure 'end_date' is in date format
polling_data$end_date <- as.Date(polling_data$end_date, format = "%Y-%m-%d")

# Summary statistics for pollster
pollster_summary <- polling_data %>%
  count(pollster) %>%
  arrange(desc(n))

# Summary statistics for state
state_summary <- polling_data %>%
  count(state) %>%
  arrange(desc(n))

# Summary statistics for end_date
end_date_summary <- polling_data %>%
  summarise(
    min_date = min(end_date, na.rm = TRUE),
    max_date = max(end_date, na.rm = TRUE),
    range_days = as.numeric(max(end_date, na.rm = TRUE) - min(end_date, na.rm = TRUE))
  )

# Display the results
kable(pollster_summary)
kable(state_summary)
kable(end_date_summary)
```

# Appendix D: Multi-Linear Regression Result {#sec-appd}

This is a multiple linear regression that runs pct on end_date, pollster, and state. The regression equation is $pct = \alpha + \beta_1\cdot \text{end\_date}+ \beta_2\cdot \text{pollster}+ \beta_3\cdot \text{state} + \epsilon$.

```{r}
#| warning: false
#| message: false
#| label: fig-figure7
#| fig-cap: "Summary of Multi-Linear Regression: Key Statistics"
#| fig_caption: true
#| echo: false

# Run the linear model
linear <- lm(pct ~ end_date + pollster + state, data = polling_data)

# Extract summary information
sumlinear <- summary(linear)

# Extract R-squared and other statistics
r_squared <- sumlinear$r.squared
adj_r_squared <- sumlinear$adj.r.squared
f_statistic <- sumlinear$fstatistic[1]

# Create a summary statistics data frame
model_summary <- data.frame(
  Statistic = c("R-squared", "Adjusted R-squared", "F-statistic"),
  Value = c(r_squared, adj_r_squared, f_statistic)
)

kable(model_summary)
```
